### 2009-06-16 paper.tex
Moved algorithms into main text

In our tests, incorporation of basepair structure was the most important factor for accurate inference of alignment;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Posterior-decoding heuristics can be substantially faster than exact phylogenetic inference,
so this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics where possible.
We discuss the use of transducer composition for ML (or MCMC) inference on phylogenies,
including possible ways to make these phylogenetic inferences tractable.

>>>>

In our tests, incorporation of basepair structure was the most important factor for accurate inference of alignment;
appropriate use of posterior-decoding was the next most important factor;
and fine details of the model were least important.
Posterior-decoding heuristics can be substantially faster than exact phylogenetic inference,
so this motivates the use of sum-over-pairs (and approximate sum-over-pairs) heuristics where possible.
For more exact probabilistic inference, we discuss the use of transducer composition for ML (or MCMC) inference on phylogenies,
including possible ways to make the core operations tractable.
